Viscous Erosion in Porous Media

### 2018-03-23 docs/methods/erosion_methods.tex
NM

	As the body shrinks in accordance with \eqref{area_predict}, the drag that it exerts decreases at a related rate, which offers a second check on our numerics. In Fig.~\ref{area_drag}(b), we show the horizontal drag, $F_D$, on the simulated body as it erodes. The drag is calculated using ...

	Figure~\ref{area_drag}(b) shows the horizontal drag, $F_D$, measured in the simulations (black curve) using Eq.~\eqref{eqn:drag}. In the context of slender-body theory, $F_D$ should be interpreted as drag-per-unit-span. As seen in Fig.~\ref{area_drag}(b), the drag decreases gradually at first and then abruptly tends to zero in the very final moments. This behavior, though perhaps surprising, is consistent with the fact that drag vanishes {\em logarithmically} with body-size in 2D Stokes flow. Equation \eqref{eqn:drag} also allows us to calculate the separate contributions of pressure and viscous drag, and we show these with the blue and green curves in Fig.~\ref{area_drag}(b). Initially, pressure and viscous drag are comparable, with the circular geometry having a slightly higher level of pressure drag. As the body erodes and assumes a more slender form, though, the pressure drag decreases much more rapidly, leaving viscous drag to dominate. This behavior is associated with the tendency towards a drag-minimizing profile, which will be discussed in Section \ref{LimitingShape}.

>>>>

	As the body shrinks in accordance with \eqref{area_predict}, the drag that it exerts decreases at a related rate, which offers a second check on our numerics. In Fig.~\ref{area_drag}(b), we show the horizontal drag on the simulated body as it erodes (black curve). The drag, $F_D$, is calculated using \eqref{eqn:drag} and, in the context of slender-body theory, should be interpreted as the drag-per-unit-span on a 2D cross-section. As seen in the figure, $F_D$ decreases gradually at first, then abruptly tends to zero in the final moments as the vanishes. This behavior, though perhaps surprising, is consistent with the fact that drag vanishes {\em logarithmically} with body-size in 2D Stokes flow. Equation \eqref{eqn:drag} also allows us to calculate the separate contributions of pressure and viscous drag, and we show these with the blue and green curves in Fig.~\ref{area_drag}(b). Initially, pressure and viscous drag are comparable, with the circular geometry having a slightly higher level of pressure drag. As the body erodes and assumes a more slender form, though, the pressure drag decreases much more rapidly, leaving viscous drag to dominate. This behavior is associated with the tendency towards a drag-minimizing profile, which will be discussed in Section \ref{LimitingShape}.
